---
title: "Coursera_DevDataProducts_RmdLeaflet"
author: "Thomas Goeppert"
date: "7 6 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!


# Load PACKAGE

```{r}
library(leaflet)
```

# Create MAP - lets have a look where I live

```{r}

geomData <- data.frame(lat = 48.40476, long = 8.01433, desc = "Gengenbach - This is my home town")

map <- leaflet() %>% 
            addTiles() %>% 
            addMarkers(lng = geomData$long ,lat = geomData$lat,popup = geomData$desc)

map

```

# Create second MAP - lets have a look at two neighbour Cities and circle size of population

```{r}

geomDataNeighb <- data.frame(lat = c(48.40476,48.4639,48.4), long = c(8.01433,7.9313,7.9833), desc = c("Gengenbach","Offenburg","Berghaupten"), pop = c(11000, 60000,2400))

mapNeighb <- leaflet() %>% 
            addTiles() %>% 
            addCircles(lng = geomDataNeighb$long, lat = geomDataNeighb$lat,  popup = geomDataNeighb$desc, radius = sqrt(geomDataNeighb$pop)*20)

mapNeighb

```

